---
title: "R Notebook"
output: html_notebook
---



```{r}
df <- read.csv("C:/Users/Gauri/OneDrive/Desktop/DS_lab/cp/Shark Tank India_modified dataset(2).csv")
print(df)

```
```{r}

dim(df)
```

```{r}
column_names <- names(df)
print(column_names)
column_names <- colnames(df)
print(column_names)
```
```{r}
missing_counts <- colSums(is.na(df))
print(missing_counts)

```
##Q1.From which state more pithcers visited Shark Tank India.
```{r}
pitchers_state_counts <- as.data.frame(table(df$`Pitchers.State`))
pitchers_state_counts <- data.frame(State = pitchers_state_counts$`Var1`, Count = pitchers_state_counts$Freq)
print(pitchers_state_counts)
if (!require(dplyr)) {
  install.packages("dplyr")
}

library(dplyr)

g1 <- df %>%
  group_by(Pitchers.State) %>%
  summarize(count = n())
colnames(g1) <- c("Pitchers.State", "Count")
print(g1)
library(ggplot2)

data <- data.frame(
  State = c(
    "Arunachal Pradesh", "Bihar", "Chhattisgarh", "Delhi", "Maharashtra",
    "Punjab", "Goa", "Gujarat", "Uttar Pradesh", "Haryana",
    "Madhya Pradesh", "Maharashtra", "West Bengal",
    "Himachal Pradesh", "Jammu & Kashmir", "Jharkhand", "Chhattisgarh",
    "Karnataka", "Andhra Pradesh", "Telangana", "West Bengal",
    "Kerala", "Maharashtra", "Madhya Pradesh", "Maharashtra", "Punjab",
    "Rajasthan", "Tamil Nadu", "Telangana", "Maharashtra", "Uttar Pradesh",
    "Uttarakhand", "Uttar Pradesh", "West Bengal"
  ),
  Count = c(
    1, 4, 1, 44, 1, 1, 3, 32, 1, 18, 1, 1, 1, 1, 3, 1, 1, 34, 1, 1, 1, 2, 1, 5, 92, 8, 11, 8, 12, 1, 13, 1, 1, 13
  )
)

ggplot(data, aes(x = State, y = Count)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(
    title = "Pitchers by State",
    x = "State",
    y = "Count"
  )

```
->Greater number of pithcher belongs Maharashtra state

##Q2.What is major industry for startups have visited Shark Tank India.
```{r}
g2 <- df %>%
  group_by(Industry) %>%
  summarize(count = n())
colnames(g2) <- c("Industry", "Count")
print(g2)
```

```{r}
library(ggplot2)
ggplot(data = g2, aes(x = Count, y =Industry)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90, hjust = 1)) +
  labs(
    title = "Industry Wise Startup",
    x = "Count",
    y = "Industry"
  )


```
->Food industry is much more popular in startups.

## Q3.How many starups are having yearly revenue greater than 400L and which one having the greatest revenue ?
```{r}

library(dplyr)
str(df)

# Check for NA values in the 'Yearly Revenue' column
is.na(df$`Yearly Revenue`)

# Group by 'Startup.Name' and calculate the sum of 'Yearly Revenue' while ignoring NAs
g3 <- df %>%
  group_by(`Startup.Name`) %>%
  summarise(`Yearly.Revenue` = sum(`Yearly.Revenue`, na.rm = TRUE))

# Filter for rows with 'Yearly.Revenue' greater than 400
g4 <- g3 %>% filter(`Yearly.Revenue` > 400)

# Count the number of rows in the filtered data
count <- nrow(g4)

# Create a boxplot of 'Yearly.Revenue' in the filtered data
boxplot(g4$`Yearly.Revenue`, main = "Boxplot of Yearly Revenue (Filtered)")


```
-> There are 23 startups having yearly revenue greater than 400 L

```{r}
# Load required libraries
# Load required libraries
library(plotly)
p <- plot_ly(data = df, x = ~Original.Ask.Amount, y = ~Startup.Name, text = ~Startup.Name, mode = "markers", type = "scatter") %>%
  layout(title = "Scatter Plot with Hover Text", xaxis = list(title = "Original Ask Amount"))


# Add layout settings for the plot
p <- p %>%
  layout(title = "Scatter Plot with Hover Text",
         xaxis = list(title = "Original Ask Amount"),
         yaxis = list(title = ""),
         showlegend = FALSE)

# Display the interactive plot
p


```


##Q4.What is the average range of Yearly revenue of startups are their any outliars ?
```{r}
library(ggplot2)
ggplot(g4, aes(x = `Startup.Name`, y = `Yearly.Revenue`)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  theme_minimal() +
  labs(
    title = "Yearly Revenue of Startups Greater than 400L",
    x = "Startup.Name",
    y = "Yearly.Revenue"
  ) +
  coord_flip()


```
->Average Range of yearly revenue is approximately 700 to 1500 L, there are 3 outliars.
French Crown have the highest Yearly Revenue.
```{r}

g5 <- g3[g3$Yearly.Revenue > 1, ]
library(ggplot2)
library(ggplot2)
ggplot(g5, aes(x = 1, y = `Yearly.Revenue`)) +
  geom_violin(fill = "steelblue") +
  theme_minimal() +
  labs(
    title = "Violin Plot of Yearly Revenue",
    x = "",  # Remove x-axis label
    y = "Yearly.Revenue"
  )



```


##Q.5 which greater average age type visited Shark tank india

```{r}
age_count<- table(df$'Pitchers.Average.Age')
print(age_count)
```
```{r}
library(ggplot2)
age_counts <- table(df$`Pitchers.Average.Age`)
age_df <- data.frame(Age = names(age_counts), Count = age_counts)
ggplot(age_df, aes(x = Age, y = age_count)) +
  geom_bar(stat = "identity", fill = "steelblue") +
  theme_minimal() +
  labs(
    title = "Pitcher Average Age",
    x = "Pitchers Age Group",
    y = "Count"
  ) +
  theme(axis.text.x = element_text(angle = 45, hjust = 1)) +
  theme(axis.title.x = element_text(size = 12)) +
  theme(axis.title.y = element_text(size = 12))


```
Middle age pitcher were more active in Shark Tank India

```{r}
if (!requireNamespace("cowplot", quietly = TRUE)) {
  install.packages("cowplot")
}
library(cowplot)

# Install and load the ggplot2 package
if (!requireNamespace("ggplot2", quietly = TRUE)) {
  install.packages("ggplot2")
}
library(ggplot2)

# Pie chart
pie_chart <- ggplot(df, aes(x = "", fill = total_sharks_invested)) +
  geom_bar(width = 1) +
  coord_polar(theta = "y") +
  labs(
    title = "Total Sharks Invested (Pie Chart)",
    fill = "Total Sharks Invested"
  ) +
  theme_minimal() +
  theme(axis.text = element_blank(), 
        axis.title = element_blank(),
        legend.title = element_text(size = 10),
        legend.text = element_text(size = 10))
my_colors <- c("red", "green", "blue")



```
```{r}
# Install and load the plotly library if not already installed
if (!require(plotly)) {
  install.packages("plotly")
}
library(plotly)
shark_names <- c("Aman", "Piyush", "Namita","Anupam", "Vinita","Ashneer") 
# Create data for the pie chart
pie_data <- table(df$total_sharks_invested)
labels <- names(pie_data)

# Create a data frame for the pie chart
pie_df <- data.frame(label = labels, value = as.numeric(pie_data))


# Create the 3D pie chart
fig <- plot_ly(pie_df, labels = ~shark_names, values = ~value, type = "pie", pull = 0.1) %>%
  layout(title = "Total Sharks Invested")
annotations <- list(
  x = 1, y = 1,
  showarrow = FALSE,
  xanchor = "right",
  yanchor = "top"
)
fig <- fig %>% layout(annotations = annotations)

# Display the 3D pie chart
fig


```
```{r}
# Install and load the required packages
library(plotly)
library(dplyr)

# Create the 3D scatter plot with layout settings
figure <- plot_ly(data = df, type = 'scatter3d', mode = 'markers',
                  x = ~pitcher_ask_amount, y = ~ask_equity, z = ~deal_amount,
                  marker = list(size = 8, color = ~deal_valuation, colorscale = 'Blues', 
                                colorbar = list(title = 'Deal Valuation', show = TRUE)),
                  text = ~brand_name, hovertemplate = 'Brand: %{text}<br>Investment Amount: %{x}<br>Equity Offered: %{y}<br>Deal Valuation: %{z}<extra></extra>',
                  layout = list(
                    title = "Investment Amount, Equity Offered, and Deal Valuation on Shark Tank India",
                    scene = list(
                      xaxis = list(title = "Investment Amount"),
                      yaxis = list(title = "Equity Offered"),
                      zaxis = list(title = "Deal Amount")
                    ),
                    template = "plotly_dark"
                  )
)

# Show the plot
figure

```
```{r}
#R shiny Dashboard
library(shiny)
library(shinydashboard)
library(ggplot2)
library(dplyr)

# Read data from a CSV file (Replace with your data path)
data <- read.csv("C:/Users/Gauri/OneDrive/Desktop/DS_lab/cp/Shark Tank India_modified dataset(2).csv")

# Define UI
ui <- dashboardPage(
  dashboardHeader(
    title = "Shark Tank Investors",
    titleWidth = "250px",
    tags$li(
      class = "dropdown",
      tags$a(
        href = "https://upload.wikimedia.org/wikipedia/en/6/68/Shark_Tank_Logo.jpg",
        target = "_blank",
        tags$img(src = "https://upload.wikimedia.org/wikipedia/en/6/68/Shark_Tank_Logo.jpg", height = "80px", width = "80px"),
        style = "padding: 10px 10px 10px 10px;"
      )
    )
  ),
  dashboardSidebar(
    sidebarMenu(
      menuItem("Aman Gupta", tabName = "aman", icon = icon("user")),
      menuItem("Vineeta Singh", tabName = "vineeta", icon = icon("user")),
      menuItem("Peyush Bansal", tabName = "peyush", icon = icon("user")),
      menuItem("Ashneer Grover", tabName = "ashneer", icon = icon("user")),
      menuItem("Anupam Mittal", tabName = "anupam", icon = icon("user"))
    )
  ),
  dashboardBody(
    tabItems(
      # Tab for Aman Gupta
      tabItem(
        tabName = "aman",
        fluidRow(
          box(
            title = "Overall Performance",
            width = 6,
            status = "primary",
            "This is a summary of Aman Gupta's overall performance."
          ),
          box(
            title = "Investment Success",
            width = 6,
            status = "warning",
            "This is a summary of Aman Gupta's investment success."
          )
        ),
        fluidRow(
          box(
            width = 6,
            status = "primary",
            div(
              style = "display: flex; flex-direction: column; align-items: center; text-align: center;",
              img(src = "https://encrypted-tbn0.gstatic.com/images?q=tbn:ANd9GcTugpbFWH4MU9B1rgJU_8fWQ_mdK7vSqOsKFA&usqp=CAU", height = "170px", width = "200px"),
              h2("Aman Gupta"),
              "Aman is the co-founder and chief marketing officer of an earwear audio company called boAt."
            )
          ),
          box(
            title = "Investment Industries",
            width = 6,
            status = "primary",
            plotOutput("aman_pie_chart", height = "300px")
          ),
          br(),
          box(
            title = "Total Investment",
            width = 6,
            status = "primary",
            div(
              style = "border: 1px solid black; padding: 10px;",
              p("100 L")
            )
          ),
          box(
            title = "Number of Companies",
            width = 6,
            status = "primary",
            div(
              style = "border: 1px solid black; padding: 10px;",
              p("19")
            )
          ),
          br(),
          box(
            title = "Go Back to Home",
            width = 12,
            status = "success",
            actionButton("aman_gobackbutton", "Go Back")
          )
        )
      ),

      # Tab for Vineeta Singh (Repeat a similar structure for other investors)
      tabItem(
        tabName = "vineeta",
        fluidRow(
          box(
            title = "Overall Performance",
            width = 6,
            status = "primary",
            "This is a summary of Vineeta Singh's overall performance."
          ),
          box(
            title = "Investment Success",
            width = 6,
            status = "warning",
            "This is a summary of Vineeta Singh's investment success."
          )
        ),
        fluidRow(
          box(
            width = 6,
            status = "primary",
            div(
              style = "display: flex; flex-direction: column; align-items: center; text-align: center;",
              img(src = "https://starsfolded.com/wp-content/uploads/2023/03/vineeta.jpg", height = "170px", width = "200px"),
              h2("Vineeta Singh"),
              "Vineeta Singh is an Indian entrepreneur and CEO and co-founder of Sugar Cosmetics."
            )
          ),
          box(
            title = "Investment Industries",
            width = 6,
            status = "primary",
            plotOutput("vineeta_pie_chart", height = "300px")
          ),
          br(),
          box(
            title = "Total Investment",
            width = 6,
            status = "primary",
            div(
              style = "border: 1px solid black; padding: 10px;",
              p("100 L")
            )
          ),
          box(
            title = "Number of Companies",
            width = 6,
            status = "primary",
            div(
              style = "border: 1px solid black; padding: 10px;",
              p("19")
            )
          ),
          br(),
          box(
            title = "Go Back to Home",
            width = 12,
            status = "success",
            actionButton("vineeta_gobackbutton", "Go Back")
          )
        )
      ),

      # Tabs for other investors (Peyush Bansal, Ashneer Grover, Anupam Mittal)
      tabItem(
  tabName = "peyush",
  fluidRow(
    box(
      title = "Overall Performance",
      width = 6,
      status = "primary",
      "This is a summary of Peyush Bansal's overall performance."
    ),
    box(
      title = "Investment Success",
      width = 6,
      status = "warning",
      "This is a summary of Peyush Bansal's investment success."
    )
  ),
  fluidRow(
    box(
      width = 6,
      status = "primary",
      div(
        style = "display: flex; flex-direction; column; align-items: center; text-align: center;",
        img(src = "https://im.indiatimes.in/content/2022/Feb/Peyush-Bansal-shark-tank-india-net-worth_6203b3d39e29c.jpg?w=1200&h=900&cc=1", height = "170px", width = "200px"),
        h2("Peyush Bansal"),
        "Peyush Bansal is an Indian entrepreneur and CEO and co-founder of Company LENSKART."
      )
    ),
    box(
      title = "Investment Industries",
      width = 6,
      status = "primary",
      plotOutput("peyush_pie_chart", height = "300px")
    ),
    br(),
    box(
      title = "Total Investment",
      width = 6,
      status = "primary",
      div(
        style = "border: 1px solid black; padding: 10px;",
        p("100 L")
      )
    ),
    box(
      title = "Number of Companies",
      width = 6,
      status = "primary",
      div(
        style = "border: 1px solid black; padding: 10px;",
        p("19")
      )
    ),
    br(),
    box(
      title = "Go Back to Home",
      width = 12,
      status = "success",
      actionButton("peyush_gobackbutton", "Go Back")
    )
  )
),

      tabItem(
  tabName = "ashneer",
  fluidRow(
    box(
      title = "Overall Performance",
      width = 6,
      status = "primary",
      "This is a summary of Ashneer Grover's overall performance."
    ),
    box(
      title = "Investment Success",
      width = 6,
      status = "warning",
      "This is a summary of Ashneer Grover's investment success."
    )
  ),
  fluidRow(
    box(
      width = 6,
      status = "primary",
      div(
        style = "https://cdn.inc42.com/wp-content/uploads/2023/01/Ashneer-Grover-Third-Unicorn-feature-760x570.png",
        img(src = "https://encrypted-tbn1.gstatic.com/images?q=tbn:ANd9GcS5XqVE28zO-RpDNASsux5oAt0Yj0biDumN6Jxj67FRhqY6zb1a", height = "170px", width = "200px"),
        h2("Ashneer Grover"),
        "Ashneer Grover is an Indian entrepreneur and CEO and co-founder of Company BharatPe and Grofers."
      )
    ),
    box(
      title = "Investment Industries",
      width = 6,
      status = "primary",
      plotOutput("ashneer_pie_chart", height = "300px")
    ),
    br(),
    box(
      title = "Total Investment",
      width = 6,
      status = "primary",
      div(
        style = "border: 1px solid black; padding: 10px;",
        p("100 L")
      )
    ),
    box(
      title = "Number of Companies",
      width = 6,
      status = "primary",
      div(
        style = "border: 1px solid black; padding: 10px;",
        p("19")
      )
    ),
    br(),
    box(
      title = "Go Back to Home",
      width = 12,
      status = "success",
      actionButton("ashneer_gobackbutton", "Go Back")
    )
  )
),


      tabItem(
        tabName = "anupam",
        # ... (Repeat the similar structure for Anupam Mittal)
        fluidRow(
  box(
    title = "Overall Performance",
    width = 6,
    status = "primary",
    "This is a summary of Anupam Mittal's overall performance."
  ),
  box(
    title = "Investment Success",
    width = 6,
    status = "warning",
    "This is a summary of Anupam Mittal's investment success."
  )
),
fluidRow(
  box(
    width = 6,
    status = "primary",
    div(
      style = "https://akm-img-a-in.tosshub.com/sites/visualstory/stories/2023_01/story_17060/assets/4.jpeg?time=1672822340&size=*:900",
      img(src = "https://encrypted-tbn3.gstatic.com/images?q=tbn:ANd9GcQAAV_idGTGubJ6eGz6NEQeQzcdi4ooq0_U5mmk5uyUL8z8JsS0", height = "170px", width = "200px"),
      h2("Anupam Mittal"),
      "Anupam Mittal is an Indian entrepreneur and CEO and co-founder of Company SHAADI.COM and People Group"
    )
  ),
  box(
    title = "Investment Industries",
    width = 6,
    status = "primary",
    plotOutput("anupam_pie_chart", height = "300px")
  ),
  br(),
  box(
    title = "Total Investment",
    width = 6,
    status = "primary",
    div(
      style = "border: 1px solid black; padding: 10px;",
      p("145 L")
    )
  ),
  box(
    title = "Number of Companies",
    width = 6,
    status = "primary",
    div(
      style = "border: 1px solid black; padding: 10px;",
      p("19")
    )
  ),
  br(),
  box(
    title = "Go Back to Home",
    width = 12,
    status = "success",
    actionButton("anupam_gobackbutton", "Go Back")
  )
)

      )
    )
  )
)

# Define server
server <- function(input, output, session) {
  # Define a common observer for "Go Back" buttons in each tab
  observeEvent(input$aman_gobackbutton, {
    updateTabsetPanel(session, "tabs", selected = "home")
  })
  observeEvent(input$vineeta_gobackbutton, {
    updateTabsetPanel(session, "tabs", selected = "home")
  })

  # Create a pie chart for Aman Gupta (Repeat for other investors)
  output$aman_pie_chart <- renderPlot({
    data_aman <- data %>% select(Industry, aman_decision)
    industry_counts <- count(data_aman, Industry)

    ggplot(industry_counts, aes(x = "", y = n, fill = Industry)) +
      geom_col(width = 0.5) +
      coord_polar(theta = "y") +
      labs(title = "Pie chart of industries where Aman Gupta invested")
  })

  # Create a pie chart for Vineeta Singh (Repeat for other investors)
  output$vineeta_pie_chart <- renderPlot({
    data_vineeta <- data %>% select(Industry, vineeta.decision)
    industry_counts <- count(data_vineeta, Industry)

    ggplot(industry_counts, aes(x = "", y = n, fill = Industry)) +
      geom_col(width = 0.5) +
      coord_polar(theta = "y") +
      labs(title = "Pie chart of industries where Vineeta Singh invested")
  })

  # Add similar renderPlot functions for other investors
  # ...
  output$anupam_pie_chart <- renderPlot({
    data_anupam <- data %>% select(Industry, anupam.decision)
    industry_counts <- count(data_anupam, Industry)

    ggplot(industry_counts, aes(x = "", y = n, fill = Industry)) +
      geom_col(width = 0.5) +
      coord_polar(theta = "y") +
      labs(title = "Pie chart of industries where Anupam Mittal invested")
  })
 
  output$ashneer_pie_chart <- renderPlot({
    data_ashneer <- data %>% select(Industry, ashneer.decision)
    industry_counts <- count(data_ashneer, Industry)

    ggplot(industry_counts, aes(x = "", y = n, fill = Industry)) +
      geom_col(width = 0.5) +
      coord_polar(theta = "y") +
      labs(title = "Pie chart of industries where Ashneer Grover invested")
  })

 output$peyush_pie_chart <- renderPlot({
    data_peyush <- data %>% select(Industry, peyush.decision)
    industry_counts <- count(data_peyush, Industry)

    ggplot(industry_counts, aes(x = "", y = n, fill = Industry)) +
      geom_col(width = 0.5) +
      coord_polar(theta = "y") +
      labs(title = "Pie chart of industries where Peyush Bansal invested")
  })

}

# Create Shiny app
shinyApp(ui, server)
```

